Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of TESS

### 2023-07-16 paper/ms.tex
update ms

\section{No additional power at 20~second cadence}

Going from K2 to TESS, an important discovery was that the CQV shapes
can significantly evolve, since the stars can vary over timescales of just a few minutes.
We observed a set of CQVs between 2020 and 2021 using the TESS 20-second
cadence mode (TESS DDT029).
{\bf todo: list the stars.  todo: examine the 2min vs 20sec periodograms, and summarize in a few
sentences whether any difference is there.}

\section{Chromaticity in TIC 262400835}

TIC~262400835 ($d$=174\,pc) is formally outside the scope of the
current work.  However, this CQV was observed using MuSCAT2 on 2020
December 12, 13, and 16, and the results might be worth including in
this study.
{\bf todo: describe observations / decide whether to include!}.

We include {\bf a table of the photometry} here to enable potential
future deeper analyses of the chromaticity of this object class.

Generally, these data serve as a minor addition beyond the
observations that have been acquired by
\citet[e.g.][]{2017PASJ...69L...2O,2020PASJ...72...23T,2022AJ....163..144G,2023MNRAS.518.2921K}
on this topic.  \citet{2023MNRAS.518.2921K} provides what we find to
be the most lucid summary, and we quote: ``amplitudes are almost
always larger, the shorter the wavelength of the filter, but the
relationship can be weak or non-monotonic.''

\begin{figure*}[!t]
	\begin{center}
    \includegraphics[width=0.45\textwidth]{TIC262400835_multicolor_phase_stacked.pdf}
    	\end{center}
    \vspace{-0.4cm}
		\caption{
	      {\bf Chromaticity in TIC~262400835}.
		}
		\label{fig:muscat}
\end{figure*}

>>>>

\section{No significant power at 20~second cadence}

TESS was the first instrument to show that CQV light curves contain
power at timescales of a few minutes
\citep{127Z,2020AJ....160...86B,2022AJ....163..144G}.  This advance
was primarily enabled by the fifteen-fold faster cadence in the TESS
2-minute data, relative to K2.

A logical follow-up question to ask is whether the periodic components
of the CQV light curves contain power at timescales below one minute.
Between 2020 and 2021, we observed 10 CQVs at 20-second cadence with
TESS in order to explore this question (TESS DDT029).  The stars were
TICs 142173958, 146539195, 24518895, 276453848, 264599508, 363963079,
144486786, 408188366, 300651846, 262400835.  The general conclusion
derived from comparing the 20-second to 120-second data for these
stars (available on MAST) was that CQVs do not contain appreciable
power at this timescale.

% \section{Chromaticity in TIC 262400835}
% 
% TIC~262400835 ($d$=174\,pc) is formally outside the scope of the
% current work.  However, this CQV was observed using MuSCAT2 on 2020
% December 12, 13, and 16, and the results might be worth including in
% this study.
% {\bf todo: describe observations / decide whether to include!}.
% 
% We include {\bf a table of the photometry} here to enable potential
% future deeper analyses of the chromaticity of this object class.
% 
% Generally, these data serve as a minor addition beyond the
% observations that have been acquired by
% \citet[e.g.][]{2017PASJ...69L...2O,2020PASJ...72...23T,2022AJ....163..144G,2023MNRAS.518.2921K}
% on this topic.  \citet{2023MNRAS.518.2921K} provides what we find to
% be the most lucid summary, and we quote: ``amplitudes are almost
% always larger, the shorter the wavelength of the filter, but the
% relationship can be weak or non-monotonic.''
% 
% \begin{figure*}[!t]
% 	\begin{center}
%     \includegraphics[width=0.45\textwidth]{TIC262400835_multicolor_phase_stacked.pdf}
%     	\end{center}
%     \vspace{-0.4cm}
% 		\caption{
% 	      {\bf Chromaticity in TIC~262400835}.
% 		}
% 		\label{fig:muscat}
% \end{figure*}
